---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Claire Chang
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(ggplot2)

data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

```

# Introduction

You can and should cross-reference sections and sub-sections. We use @talia, @opendatatorotno, and @rohan.

The remainder of this paper is structured as follows. @sec-mydatasection

# Data {#sec-mydatasection}

Some of our data is of penguins (@fig-marriage), from @palmerpenguins.

```{r}
#| label: fig-marriage
#| fig-cap: Bills of penguins
#| echo: false

data |> 
  ggplot(aes(x = date, y = marriage_licenses)) +
  geom_point()

```

Talk more about it: The scatter plot displays the distribution of marriage licenses issued over time, showing a generally consistent pattern with a noticeable increase in the number of licenses issued starting around 2020.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
# Load the necessary library
library(tidyverse)

# Assuming your data is in a dataframe called 'raw_data', inspect the data first
head(data)

# Create a bar chart: count of marriage licenses by civic center
ggplot(data, aes(x = civic_centre, y = marriage_licenses)) +
  geom_bar(stat = "identity", fill = "steelblue") +  # Change 'steelblue' to any desired color
  labs(
    title = "Marriage Licenses Issued by Civic Center",
    x = "Civic Centre",
    y = "Number of Marriage Licenses"
  ) +
  theme_minimal() +  # Optional: for a clean theme
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate x-axis labels if needed
```

The bar chart shows the distribution of marriage licenses issued at different civic centers. Toronto (TO) has a noticeably higher number of licenses compared to Scarborough (SC), North York (NY), and Etobicoke (ET), suggesting that TO handles a substantially greater volume of marriage licenses than the other locations.

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {.unnumbered}

# Additional data details

\newpage

# References
